On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-22 techreport.tex
Clarify based on Review 4's item 3.
Make n-truthful become $N$-truthful, because n is used as number of sensing tasks. Here $N$ denotes the entire user population. Hope it clarifies.

{\color{black}
\begin{abstract}
%With the rise of smartphones, crowdsensing applications have tremendously increasing trending. As a result, many incentive and privacy issues are worth researching. This paper gives detailed discussions on collusion resistant incentive mechanisms for crowdsensing applications. We analyze the continuous crowdsensing game in which users take sensing time to finish tasks and get payment. Two fundamental criteria are found: one is to judge whether a truthful incentive mechanism can resist any collusion without profit trading by achieving group strategyproof equilibrium, and the other is to judge whether a truthful mechanism can defend against any collusion even with profit trading by achieving n-truthful equilibrium. We also propose a concrete solution that not only satisfies both the criteria, but also maximizes the platform utility. However, sometimes users can only finish the sensing in discretized units and thus the continuous sensing time assumption may not hold any more. To address this discrete scenario, we give detailed analysis and propose a heuristic incentive solution that not only resists any collusion attack, but also preserves differential privacy of the participatory users. Extensive simulations verify our results. To the best of our knowledge, we are the first to investigate the collusion resistant incentive mechanisms for crowdsensing applications.

@@

\bolditem We investigate a popular type of crowdsensing games, in which each contributing user takes some sensing time to finish the assigned tasks and earns the promised payment from the platform. We not only find it is feasible to design group strategyproof incentive mechanisms for this type of crowdsensing game, but also obtain the straightforward criteria to judge whether a given strategy-proof incentive mechanism can achieve group strategyproofness. Moreover, we rigorously derive the criteria to judge whether a truthful mechanism is t-truthful to guard against profit trading. %In other words, we show that it is theoretically possible to resist any collusion attack, even with profit trading, for the crowdsensing game. 
%By correctly judging whether an incentive mechanism can resist collusion or profit trading, we can gain many benefits in the real world. For example, \cite{archer2004approximation} has given the truthful incentive mechanism that can successfully defend against collusion in multicast cost sharing by achieving group strategyproofness. If each user cannot trust others completely, the information from the users can be reliable and the system does not have to use extra protocols to ensure no one is cheating. In this light, we can obtain reliable information and save communication overhead if we can show the truthful incentive mechanism can achieve group strategyproofness. %For the scenario of wireless ad hoc routing, \cite{zhong2007designing} has given the collusion resistant incentive mechanism that cannot achieve n-truthfulness. That is, their proposed incentive mechanism cannot solely eliminate the possibility of profit trading. This implies that one has to take additional actions to rigorously defend against profit trading, for example, by leveraging some public cryptographic protocols such as Designated Verifier Signatures \cite{jakobsson1996designated} or Restricted Verifier Signatures \cite{zhong2007designing}. In other words, if we can show the incentive mechanism can intrinsically defend against profit trading by achieving n-truthfulness, then we do not have to use the extra cryptographic protocols and hence reduce the computation and communication overhead. Hence our obtained criteria can give practical benefits.} %Furthermore, based on both the obtained criteria, we propose a concrete incentive mechanism which is not only collusion resistant, but also maximizes the platform utility.

@@

%\bolditem {\color{black}Privacy issues in crowdsensing have attracted extensive researchers' attention \cite{agarwal2013protectmyprivacy, varshney2012privacy}. We take the threat model in which the attacker may know the number of assigned tasks to each user by traffic analysis or timing attacks. While assuming the sensing cost and the identity of each user should be private, we propose a new discrete incentive mechanism, and rigorously show that this proposed mechanism not only can achieve group strategyproofness and n-truthfulness, but also can preserve 0-differential privacy.} Hence our proposed mechanism for discrete incentives not only can resist any collusion (even with profit trading), but also can well preserve the users' privacy.

@@

%The remainder of this paper is organized as follows. Section \ref{sec:TP} gives the necessary technical preliminaries including equilibria, collusion attack, profit trading and differential privacy. Section \ref{sec:PFSM} discusses the basic settings of the crowdsensing game model. Section \ref{sec:GSIM} gives the criteria whether a truthful crowdsensing incentive mechanism can be group strategyproof. Section \ref{sec:DFPT} gives the criteria whether a truthful mechanism can be n-truthful. Section \ref{sec:opu} proposes our concrete continuous collusion resistant incentive mechanism that can also maximize the platform utility. In Section \ref{sec:discrete} we propose the discrete collusion resistant incentive mechanism, and then give discussions on the incentive and privacy issues on the discrete crowdsensing game. We also propose our heuristic solutions to eliminate some singular privacy leakage cases. Section \ref{sec:sim} gives the simulation results and Section \ref{sec:rw} summarizes the related literatures. Section \ref{sec:con} concludes this paper.

@@

\section{Technical Preliminaries}
\label{sec:TP}
This section describes the technical preliminaries including the basics of crowdsensing game, the concept of equilibrium in game theory, and the idea of profit trading. We also give some useful local properties of bivariate functions in the appendix. Table \ref{tab:symbol_list} presents the frequently used symbols in this paper.\footnotetext[1]{Similarly, by removing subscripts, $t$ denotes the sensing time profile, $p$ denotes the payment profile, $u$ denotes the user utility profile, $n$ denotes the profile of number of tasks, etc.}
\begin{table}[!t]
\caption{Frequently used notations}
\label{tab:symbol_list}
\begin{tabular}{l l}
\toprule
Notation & Description\\
\hline
$U$ & the set of users\\
$n$ & the number of users: $|U|$ \\
%$R$ & the baseline gain of the platform\\
$s_i$ & the claimed cost unit (strategy) of user $i$\\
$s$ & the strategy profile of all users \footnotemark[1]\\
$s_{-i}$ & the strategy profile excluding user $i$'s strategy\\
$\kappa_i$ & the cost unit of user $i$\\
$p_i$ & the (promised) payment to user $i$\\
$t_i$ & the required sensing time of user $i$\\
$u_i$ & the utility function of user $i$\\
$u_p$ & the utility function of the platform\\
$n_i$ & number of the assigned tasks to user $i$\\
$m$	& number of partitions\\
$d$ & partition length\\
$f(x, y_0)$ & the slice function of $f(x,y)$ by fixing $y = y_0$\\
$B$ & budget, upper bound of the payment sum $\sum p_i$\\
$R$ & the number of remaining sensing tasks to do\\
\bottomrule
\smallskip
\end{tabular}
\end{table}
\addtocounter{footnote}{1}

\subsection{Crowdsensing Game}
\label{subsec:CG}
{
We introduce the general game model of crowdsensing system, which is used in the majority of existing literatures \cite{yang2012crowdsourcing,koutsopoulos2013optimal,luo2014profit,zhang2014free,liu2014social,yan2015ifc}. The crowdsensing system consists of $n$ participating users, who are all the users \emph{willing} to contribute in the crowdsensing work (e.g. smartphones, mobile sensors) and one crowdsensing platform (e.g. BOINC \cite{anderson2004boinc}). The $n$ users voluntarily participate in crowdsensing and contribute their sensing results. The platform aggregates the sensing results from the $n$ users and maintains the crowdsensing system. %For each contributing user\footnote{contributing users are the users who \emph{actually} participate in the crowdsensing by \emph{contributing} sensing work.}, sensing work incurs cost in monetary form, such as battery charge and communication fees. 
To compensate the users' sensing costs and stimulate their participation, the platform distributes some payment to each user as the reward. The payment is determined by each user's strategy (i.e., its claimed sensing cost). Denote by $c_i$ the sensing cost of user $i$, and let $p_i$ be the promised payment from the platform to user $i$. If user $i$ can complete the sensing task as promised, then the utility of user $i$ is
\begin{equation}
\label{eqn:user_utility_1}
u_i = p_i-c_i.
\end{equation}
%Here the utility is the incentive for each user to participate in crowdsensing. 
Due to individual rationality, each user wants to maximize its own utility. %To address the incentive issues, we need an incentive mechanism, which is an interactive scheme between the users and the platform to determine the payment to each user.

@@

To eradicate collusion, we have the standard game theoretic solution concept of Group Strategyproof Equilibrium as follows.}
\begin{definition}
\label{def:gse}
\textbf{(Group Strategyproof Equilibrium)} \cite{jain1999group} \cite{moulin2001strategyproof}. Let $U$ be the set of all the players. A strategy profile $s^*$ is Group Strategyproof Equilibrium if for any nonempty subset $S\subseteq U$, for any strategy profile $s$, either for any $i\in S$, we have
\begin{equation}
u_i(s_S^*,s_{\overline{S}})=u_i(s_S,s_{\overline{S}}),
\end{equation}
or there exists a user $i\in S$ s.t.
\begin{equation}
u_i(s_S^*,s_{\overline{S}})>u_i(s_S,s_{\overline{S}}).
\end{equation}
Here $s^*=\kappa$, the real cost profile.
\end{definition}
When an equilibrium is group strategyproof, if a subset of users change their strategies simultaneously, either none of them can gain more utility, or some of them have their utilities decreased. In fact, group strategyproof equilibrium can make any collusion without profit trading among the users fail \cite{zhong2007designing}.

@@

\section{Defense Against Profit Trading By n-Truthfulness}
\label{sec:DFPT}
In this section, we talk about how to defend against profit trading collusion in the strategyproof crowdsensing game. We have demonstrated that group strategyproof equilibrium can not guarantee profit trading free in Section \ref{subsec:pt}. We next research the criteria in which the strategyproof mechanism can resist any profit trading collusion. The result is Theorem \ref{thm:pt}.
\begin{theorem}
\label{thm:pt}
For any strategyproof crowdsensing incentive mechanism with user utility equation (\ref{eqn:user_utility_2}), the mechanism can achieve $n$-Truthfulness, where $n$ denotes the number of all the participating users: $n=|U|$, if and only if its parametric dependency graph $G=(U,E)$ satisfies $E=\emptyset$.
\end{theorem}
\begin{IEEEproof}
We first show the necessity by proving the contrapositive. That is, there may exist a couple of users that may collude to trade profit, if there is at least one edge in the PDG of the game. We may assume there exists one edge from user $i$ to $j$ in the PDG, indicating $u_i$ is parametric dependent on $s_j$. Note that it is impossible to have a path from $j$ to $i$. Otherwise, the PDG is cyclic and thus there must exist a subset of users that may succeed to collude based on Lemma \ref{lem:bf}. In fact, the collusion here is valid without profit trading, since cyclic PDG means there is no means to achieve group strategyproof equilibrium in order to resist collusion. Then we have
\begin{equation}
\label{eqn:uij}
\begin{aligned}
&\frac{\partial u_i}{\partial s_i}(\kappa_i,\kappa_j)=0, \quad \frac{\partial u_i}{\partial s_j}(\kappa_i,\kappa_j)\not=0;\\
&\frac{\partial u_j}{\partial s_i}(\kappa_i,\kappa_j)=0, \quad \frac{\partial u_j}{\partial s_j}(\kappa_i,\kappa_j)=0.
\end{aligned}
\end{equation}
Let $u_{ij}$ be the total utility of users $i,j$: $u_{ij}=u_i+u_j$. Based on (\ref{eqn:uij}), we have
\begin{equation}
\frac{\partial u_{ij}}{\partial s_i}(\kappa_i,\kappa_j)=0, \quad \frac{\partial u_{ij}}{\partial s_j}(\kappa_i,\kappa_j)\not=0.
\end{equation}
According to Lemma \ref{lem:bf}, there always exist uncountably infinite points $(s_i,s_j)\not=(\kappa_i,\kappa_j)$ such that $u_{ij}(s_j,s_j)>u_{ij}(\kappa_i,\kappa_j)$. Thus, users $i,j$ may collude to trade profit.

We next show the sufficiency. Since there is no edge in the PDG, any user utility is not parametric dependent on any other user\rq{}s strategy. That is, each user can maximize its utility, as long as it strategizes truthfully. Then for any $s$, for any subset $S\subseteq U$, we have
\begin{equation}
\sum_{i\in S}u_i(s_S,s_{\overline{S}})\leq \sum_{i\in S}u_i(\kappa_i,s_{-i}) = \sum_{i\in S}u_i(\kappa_S,s_{\overline{S}}),
\end{equation}
which shows the mechanism must achieve n-Truthfulness.
\end{IEEEproof}
{\color{black}
The result of Theorem \ref{thm:pt} is slightly pessimistic, since it requires the PDG must have no edges to achieve n-Truthfulness. But it is not always necessary. The condition of n-Truthfulness (Definition \ref{def:tt}) is so strong that it assumes each colluded user may offer full trust to any other conspirator. However, in real-world crowdsensing applications, it is not always that all users share the unconditional trust when colluding. If there is no such complete trust, it is fine to have some edges (no cycles) in the PDG.
}

%\section{Concrete Incentive Mechanism By Optimizing the Platform Utility}
%\label{sec:opu}
%The previous sections have discussed our incentive mechanism from the users\rq{} aspect. In this section we will give the solution to optimize the design of the platform utility. We show that we can maximize the platform utility as (\ref{eqn:plat_utility}) by giving the closed-form of the required sensing time of each user.
%
%Based on (\ref{eqn:payment}), we calculate the partial derivatives of (\ref{eqn:plat_utility}):
%\begin{equation}
%\frac{\partial u_p}{\partial s_i}=\frac{\mathrm{d} t_i(s_i)}{\mathrm{d} s_i}\left( \frac{\lambda_i}{1+t_i(s_i)}-s_i\right).
%\end{equation}
%Since we already demand the required sensing time is monotonically decreasing as the strategy $s_i$ increases, we have $\frac{\mathrm{d} t_i(s_i)}{\mathrm{d} s_i}<0$. By letting $\frac{\lambda_i}{1+t_i(s_i)}-s_i=0$, we have $\frac{\partial u_p}{\partial s_i}=0$ and thus satisfy one of the conditions of maxima. Consequently, we determine the closed-form of $t_i(s_i)$:\footnote{Mathematically, the function $t_i(s_i)$ is not differentiable at $s_i=\lambda_i$. Fortunately, since $t_i(\lambda_i)=0$, we already exclude this user from participating, and thus it does not affect our results.}
%\begin{equation}
%\label{eqn:ti}
%t_i(s_i) = 
	%\begin{cases}
		%\frac{\lambda_i}{s_i}-1 & 0<s_i<\lambda_i, \\
		%0 & s_i\geq\lambda_i.
	%\end{cases}
%\end{equation}
%The construction idea of $t_i$ here is that we firstly eliminate the users whose claimed costs are too high (say, higher than $\lambda_i$), and then calculate the payments based on the reciprocal equation in (\ref{eqn:ti}) for the rest users. By setting $t_i$ like (\ref{eqn:ti}), we have $u_p=R>0$. {\color{black}That is, the platform can receive the constant reward $R$ and thus a positive baseline reward $R$ can guarantee a positive platform utility.} Then the platform can calculate the payment to each user by the following elegant equation:
%\begin{equation}
%p_i(s_i)=
	%\begin{cases}
		%\lambda_i\log \frac{\lambda_i}{s_i} & 0<s_i<\lambda_i, \\
		%0 & s_i\geq\lambda_i.
	%\end{cases}
%\end{equation}
%It is easy to verify that this optimized mechanism can achieve not only group strategyproof equilibrium, but also n-Truthfulness. Thus it is a desirable solution to defend against collusion, while maximizing user and platform utilities.

@@

In this section, we will give our discrete crowdsensing incentive mechanism that can resist collusion attacks, even including profit trading. We will also rigorously show that our mechanism can achieve group strategyproof and n-truthful equilibrium.

@@

%In this section we discuss the collusion resistant incentive mechanism for discrete crowdsensing. We will firstly state the assumptions formally and then propose the incentive mechanism. We will show our mechanism is group strategyproof and n-truthful. %Finally we will show our mechanism can well preserve 0-differential privacy for certain user groups. 
%Our results verify the fact that our discrete solution not only can resist any collusion, even including profit trading.%, but also can very well preserve the privacy of each participatory user.

@@

Note that in many practical applications, the total number of discrete sensing tasks is upper bounded \cite{Alt2010Location,Liu2013A,li2012location}. We also assume the payment sum is upper bounded by the budget $B$. To upper bound each $n_i$, we introduce $P_m$, the maximum payment to any user. Let $n$ be the number of participating users. Then we require $B\geq nP_m$. On the other hand, for each user, the assigned number of sensing tasks cannot exceed the number of remaining tasks to do. Otherwise, the platform will not allow the user to do any task. This is reflected by the threshold $R$, the number of remaining tasks in Algorithm \ref{alg:np}.
}

@@

{\color{black}
\subsection{Proofs of Collusion and Profit Trading Resistance}
We now show that Algorithm \ref{alg:np} can not only resist collusion attacks (by achieving group strategyproofness), but also eradicate the possibility of any profit trading (by achieving n-truthfulness). Parametric Dependency Graph (PDG) will be used to judge whether the strategyproof equilibrium can be group strategyproof or n-truthful.

@@

%Firstly our mechanism can achieve group strategyproof and n-truthful equilibrium.

@@

%For any discrete crowdsensing game with user utility equation $u_i = p_i - \kappa_in_i$, the incentive mechanism given above can achieve group strategyproof and n-truthful equilibrium.

@@

{\bf Budget utilization}. We first consider the budget utilization ratio of our mechanism with different sizes of users. Figure \ref{fig:rho_n} gives the results. The budget utilization ratio decreases as the size of users grows, since the maximum payment $P_m$ will decrease given more participating users ($nP_m$ is bounded by the budget $B$). In our mechanism, usually the budget utilization ratio is less than 16\%, which is budget-feasible. Repeating our mechanism may amplify the ratio. Since there are abundant budget, we can repeat the game many times.

@@

%This section will show our simulations that support the theoretic results we have obtained in the previous sections. Our crowdsensing incentive mechanism can achieve group strategyproof and n-truthful equilibrium simultaneously. 

>>>>

{\color{black}
\begin{abstract}
%With the rise of smartphones, crowdsensing applications have tremendously increasing trending. As a result, many incentive and privacy issues are worth researching. This paper gives detailed discussions on collusion resistant incentive mechanisms for crowdsensing applications. We analyze the continuous crowdsensing game in which users take sensing time to finish tasks and get payment. Two fundamental criteria are found: one is to judge whether a truthful incentive mechanism can resist any collusion without profit trading by achieving group strategyproof equilibrium, and the other is to judge whether a truthful mechanism can defend against any collusion even with profit trading by achieving $N$-truthful equilibrium. We also propose a concrete solution that not only satisfies both the criteria, but also maximizes the platform utility. However, sometimes users can only finish the sensing in discretized units and thus the continuous sensing time assumption may not hold any more. To address this discrete scenario, we give detailed analysis and propose a heuristic incentive solution that not only resists any collusion attack, but also preserves differential privacy of the participatory users. Extensive simulations verify our results. To the best of our knowledge, we are the first to investigate the collusion resistant incentive mechanisms for crowdsensing applications.

@@

\bolditem We investigate a popular type of crowdsensing games, in which each contributing user takes some sensing time to finish the assigned tasks and earns the promised payment from the platform. We not only find it is feasible to design group strategyproof incentive mechanisms for this type of crowdsensing game, but also obtain the straightforward criteria to judge whether a given strategy-proof incentive mechanism can achieve group strategyproofness. Moreover, we rigorously derive the criteria to judge whether a truthful mechanism is t-truthful to guard against profit trading. %In other words, we show that it is theoretically possible to resist any collusion attack, even with profit trading, for the crowdsensing game. 
%By correctly judging whether an incentive mechanism can resist collusion or profit trading, we can gain many benefits in the real world. For example, \cite{archer2004approximation} has given the truthful incentive mechanism that can successfully defend against collusion in multicast cost sharing by achieving group strategyproofness. If each user cannot trust others completely, the information from the users can be reliable and the system does not have to use extra protocols to ensure no one is cheating. In this light, we can obtain reliable information and save communication overhead if we can show the truthful incentive mechanism can achieve group strategyproofness. %For the scenario of wireless ad hoc routing, \cite{zhong2007designing} has given the collusion resistant incentive mechanism that cannot achieve $N$-truthfulness. That is, their proposed incentive mechanism cannot solely eliminate the possibility of profit trading. This implies that one has to take additional actions to rigorously defend against profit trading, for example, by leveraging some public cryptographic protocols such as Designated Verifier Signatures \cite{jakobsson1996designated} or Restricted Verifier Signatures \cite{zhong2007designing}. In other words, if we can show the incentive mechanism can intrinsically defend against profit trading by achieving $N$-truthfulness, then we do not have to use the extra cryptographic protocols and hence reduce the computation and communication overhead. Hence our obtained criteria can give practical benefits.} %Furthermore, based on both the obtained criteria, we propose a concrete incentive mechanism which is not only collusion resistant, but also maximizes the platform utility.

@@

%\bolditem {\color{black}Privacy issues in crowdsensing have attracted extensive researchers' attention \cite{agarwal2013protectmyprivacy, varshney2012privacy}. We take the threat model in which the attacker may know the number of assigned tasks to each user by traffic analysis or timing attacks. While assuming the sensing cost and the identity of each user should be private, we propose a new discrete incentive mechanism, and rigorously show that this proposed mechanism not only can achieve group strategyproofness and $N$-truthfulness, but also can preserve 0-differential privacy.} Hence our proposed mechanism for discrete incentives not only can resist any collusion (even with profit trading), but also can well preserve the users' privacy.

@@

%The remainder of this paper is organized as follows. Section \ref{sec:TP} gives the necessary technical preliminaries including equilibria, collusion attack, profit trading and differential privacy. Section \ref{sec:PFSM} discusses the basic settings of the crowdsensing game model. Section \ref{sec:GSIM} gives the criteria whether a truthful crowdsensing incentive mechanism can be group strategyproof. Section \ref{sec:DFPT} gives the criteria whether a truthful mechanism can be $N$-truthful. Section \ref{sec:opu} proposes our concrete continuous collusion resistant incentive mechanism that can also maximize the platform utility. In Section \ref{sec:discrete} we propose the discrete collusion resistant incentive mechanism, and then give discussions on the incentive and privacy issues on the discrete crowdsensing game. We also propose our heuristic solutions to eliminate some singular privacy leakage cases. Section \ref{sec:sim} gives the simulation results and Section \ref{sec:rw} summarizes the related literatures. Section \ref{sec:con} concludes this paper.

@@

\section{Technical Preliminaries}
\label{sec:TP}
This section describes the technical preliminaries including the basics of crowdsensing game, the concept of equilibrium in game theory, and the idea of profit trading. We also give some useful local properties of bivariate functions in the appendix. Table \ref{tab:symbol_list} presents the frequently used symbols in this paper.\footnotetext[1]{Similarly, by removing subscripts, $t$ denotes the sensing time profile, $p$ denotes the payment profile, $u$ denotes the user utility profile, $n$ denotes the profile of number of tasks, etc.}
\begin{table}[!t]
\caption{Frequently used notations}
\label{tab:symbol_list}
\begin{tabular}{l l}
\toprule
Notation & Description\\
\hline
$U$ & the set of users\\
$N$ & the number of users: $|U|$ \\
%$R$ & the baseline gain of the platform\\
$s_i$ & the claimed cost unit (strategy) of user $i$\\
$s_S$ & the strategy profile on the user subtask $S$\\
$s$ & the strategy profile of all users \footnotemark[1]\\
$s_{-i}$ & the strategy profile excluding user $i$'s strategy\\
$\kappa_i$ & the cost unit of user $i$\\
$p_i$ & the (promised) payment to user $i$\\
$t_i$ & the required sensing time of user $i$\\
$u_i$ & the utility function of user $i$\\
$u_p$ & the utility function of the platform\\
$n_i$ & number of the assigned tasks to user $i$\\
$m$	& number of partitions\\
$d$ & partition length\\
$f(x, y_0)$ & the slice function of $f(x,y)$ by fixing $y = y_0$\\
$B$ & budget, upper bound of the payment sum $\sum p_i$\\
$R$ & the number of remaining sensing tasks to do\\
\bottomrule
\smallskip
\end{tabular}
\end{table}
\addtocounter{footnote}{1}

\subsection{Crowdsensing Game}
\label{subsec:CG}
{
We introduce the general game model of crowdsensing system, which is used in the majority of existing literatures \cite{yang2012crowdsourcing,koutsopoulos2013optimal,luo2014profit,zhang2014free,liu2014social,yan2015ifc}. The crowdsensing system consists of $N$ participating users, who are all the users \emph{willing} to contribute in the crowdsensing work (e.g. smartphones, mobile sensors) and one crowdsensing platform (e.g. BOINC \cite{anderson2004boinc}). The $N$ users voluntarily participate in crowdsensing and contribute their sensing results. The platform aggregates the sensing results from the $N$ users and maintains the crowdsensing system. %For each contributing user\footnote{contributing users are the users who \emph{actually} participate in the crowdsensing by \emph{contributing} sensing work.}, sensing work incurs cost in monetary form, such as battery charge and communication fees. 
To compensate the users' sensing costs and stimulate their participation, the platform distributes some payment to each user as the reward. The payment is determined by each user's strategy (i.e., its claimed sensing cost). Denote by $c_i$ the sensing cost of user $i$, and let $p_i$ be the promised payment from the platform to user $i$. If user $i$ can complete the sensing task as promised, then the utility of user $i$ is
\begin{equation}
\label{eqn:user_utility_1}
u_i = p_i-c_i.
\end{equation}
%Here the utility is the incentive for each user to participate in crowdsensing. 
Due to individual rationality, each user wants to maximize its own utility. %To address the incentive issues, we need an incentive mechanism, which is an interactive scheme between the users and the platform to determine the payment to each user.

@@

To eradicate collusion, we have the standard game theoretic solution concept of Group Strategyproof Equilibrium as follows.}
\begin{definition}
\label{def:gse}
\textbf{(Group Strategyproof Equilibrium)} \cite{jain1999group} \cite{moulin2001strategyproof}. Let $U$ be the set of all the players. A strategy profile $s^*$ is Group Strategyproof Equilibrium if for any nonempty subset $S\subseteq U$, for any strategy profile $s$, either for any $i\in S$, we have
\begin{equation}
u_i(s_S^*,s_{\overline{S}})=u_i(s_S,s_{\overline{S}}),
\end{equation}
or there exists a user $i\in S$ s.t.
\begin{equation}
u_i(s_S^*,s_{\overline{S}})>u_i(s_S,s_{\overline{S}}).
\end{equation}
Here $s^*=\kappa$, the real cost profile. {\color{blue}$\overline{S}$ denotes the complementary set of $S$. $s_S$ and $s_{\overline{S}}$ denote the strategy profile on $S$ and $\overline{S}$ respectively.}
\end{definition}
When an equilibrium is group strategyproof, if a subset of users change their strategies simultaneously, either none of them can gain more utility, or some of them have their utilities decreased. In fact, group strategyproof equilibrium can make any collusion without profit trading among the users fail \cite{zhong2007designing}.

@@

\section{Defense Against Profit Trading By $N$-Truthfulness}
\label{sec:DFPT}
In this section, we talk about how to defend against profit trading collusion in the strategyproof crowdsensing game. We have demonstrated that group strategyproof equilibrium can not guarantee profit trading free in Section \ref{subsec:pt}. We next research the criteria in which the strategyproof mechanism can resist any profit trading collusion. The result is Theorem \ref{thm:pt}.
\begin{theorem}
\label{thm:pt}
For any strategyproof crowdsensing incentive mechanism with user utility equation (\ref{eqn:user_utility_2}), the mechanism can achieve $N$-Truthfulness, where $N$ denotes the number of all the participating users: $N=|U|$, if and only if its parametric dependency graph $G=(U,E)$ satisfies $E=\emptyset$.
\end{theorem}
\begin{IEEEproof}
We first show the necessity by proving the contrapositive. That is, there may exist a couple of users that may collude to trade profit, if there is at least one edge in the PDG of the game. We may assume there exists one edge from user $i$ to $j$ in the PDG, indicating $u_i$ is parametric dependent on $s_j$. Note that it is impossible to have a path from $j$ to $i$. Otherwise, the PDG is cyclic and thus there must exist a subset of users that may succeed to collude based on Lemma \ref{lem:bf}. In fact, the collusion here is valid without profit trading, since cyclic PDG means there is no means to achieve group strategyproof equilibrium in order to resist collusion. Then we have
\begin{equation}
\label{eqn:uij}
\begin{aligned}
&\frac{\partial u_i}{\partial s_i}(\kappa_i,\kappa_j)=0, \quad \frac{\partial u_i}{\partial s_j}(\kappa_i,\kappa_j)\not=0;\\
&\frac{\partial u_j}{\partial s_i}(\kappa_i,\kappa_j)=0, \quad \frac{\partial u_j}{\partial s_j}(\kappa_i,\kappa_j)=0.
\end{aligned}
\end{equation}
Let $u_{ij}$ be the total utility of users $i,j$: $u_{ij}=u_i+u_j$. Based on (\ref{eqn:uij}), we have
\begin{equation}
\frac{\partial u_{ij}}{\partial s_i}(\kappa_i,\kappa_j)=0, \quad \frac{\partial u_{ij}}{\partial s_j}(\kappa_i,\kappa_j)\not=0.
\end{equation}
According to Lemma \ref{lem:bf}, there always exist uncountably infinite points $(s_i,s_j)\not=(\kappa_i,\kappa_j)$ such that $u_{ij}(s_j,s_j)>u_{ij}(\kappa_i,\kappa_j)$. Thus, users $i,j$ may collude to trade profit.

We next show the sufficiency. Since there is no edge in the PDG, any user utility is not parametric dependent on any other user\rq{}s strategy. That is, each user can maximize its utility, as long as it strategizes truthfully. Then for any $s$, for any subset $S\subseteq U$, we have
\begin{equation}
\sum_{i\in S}u_i(s_S,s_{\overline{S}})\leq \sum_{i\in S}u_i(\kappa_i,s_{-i}) = \sum_{i\in S}u_i(\kappa_S,s_{\overline{S}}),
\end{equation}
which shows the mechanism must achieve $N$-Truthfulness.
\end{IEEEproof}
{\color{black}
The result of Theorem \ref{thm:pt} is slightly pessimistic, since it requires the PDG must have no edges to achieve $N$-Truthfulness. But it is not always necessary. The condition of $N$-Truthfulness (Definition \ref{def:tt}) is so strong that it assumes each colluded user may offer full trust to any other conspirator. However, in real-world crowdsensing applications, it is not always that all users share the unconditional trust when colluding. If there is no such complete trust, it is fine to have some edges (no cycles) in the PDG.
}

%\section{Concrete Incentive Mechanism By Optimizing the Platform Utility}
%\label{sec:opu}
%The previous sections have discussed our incentive mechanism from the users\rq{} aspect. In this section we will give the solution to optimize the design of the platform utility. We show that we can maximize the platform utility as (\ref{eqn:plat_utility}) by giving the closed-form of the required sensing time of each user.
%
%Based on (\ref{eqn:payment}), we calculate the partial derivatives of (\ref{eqn:plat_utility}):
%\begin{equation}
%\frac{\partial u_p}{\partial s_i}=\frac{\mathrm{d} t_i(s_i)}{\mathrm{d} s_i}\left( \frac{\lambda_i}{1+t_i(s_i)}-s_i\right).
%\end{equation}
%Since we already demand the required sensing time is monotonically decreasing as the strategy $s_i$ increases, we have $\frac{\mathrm{d} t_i(s_i)}{\mathrm{d} s_i}<0$. By letting $\frac{\lambda_i}{1+t_i(s_i)}-s_i=0$, we have $\frac{\partial u_p}{\partial s_i}=0$ and thus satisfy one of the conditions of maxima. Consequently, we determine the closed-form of $t_i(s_i)$:\footnote{Mathematically, the function $t_i(s_i)$ is not differentiable at $s_i=\lambda_i$. Fortunately, since $t_i(\lambda_i)=0$, we already exclude this user from participating, and thus it does not affect our results.}
%\begin{equation}
%\label{eqn:ti}
%t_i(s_i) = 
	%\begin{cases}
		%\frac{\lambda_i}{s_i}-1 & 0<s_i<\lambda_i, \\
		%0 & s_i\geq\lambda_i.
	%\end{cases}
%\end{equation}
%The construction idea of $t_i$ here is that we firstly eliminate the users whose claimed costs are too high (say, higher than $\lambda_i$), and then calculate the payments based on the reciprocal equation in (\ref{eqn:ti}) for the rest users. By setting $t_i$ like (\ref{eqn:ti}), we have $u_p=R>0$. {\color{black}That is, the platform can receive the constant reward $R$ and thus a positive baseline reward $R$ can guarantee a positive platform utility.} Then the platform can calculate the payment to each user by the following elegant equation:
%\begin{equation}
%p_i(s_i)=
	%\begin{cases}
		%\lambda_i\log \frac{\lambda_i}{s_i} & 0<s_i<\lambda_i, \\
		%0 & s_i\geq\lambda_i.
	%\end{cases}
%\end{equation}
%It is easy to verify that this optimized mechanism can achieve not only group strategyproof equilibrium, but also $N$-Truthfulness. Thus it is a desirable solution to defend against collusion, while maximizing user and platform utilities.

@@

In this section, we will give our discrete crowdsensing incentive mechanism that can resist collusion attacks, even including profit trading. We will also rigorously show that our mechanism can achieve group strategyproof and $N$-truthful equilibrium.

@@

%In this section we discuss the collusion resistant incentive mechanism for discrete crowdsensing. We will firstly state the assumptions formally and then propose the incentive mechanism. We will show our mechanism is group strategyproof and $N$-truthful. %Finally we will show our mechanism can well preserve 0-differential privacy for certain user groups. 
%Our results verify the fact that our discrete solution not only can resist any collusion, even including profit trading.%, but also can very well preserve the privacy of each participatory user.

@@

Note that in many practical applications, the total number of discrete sensing tasks is upper bounded \cite{Alt2010Location,Liu2013A,li2012location}. We also assume the payment sum is upper bounded by the budget $B$. To upper bound each $n_i$, we introduce $P_m$, the maximum payment to any user. Let $N$ be the number of participating users. Then we require $B\geq N \cdot P_m$. On the other hand, for each user, the assigned number of sensing tasks cannot exceed the number of remaining tasks to do. Otherwise, the platform will not allow the user to do any task. This is reflected by the threshold $R$, the number of remaining tasks in Algorithm \ref{alg:np}.
}

@@

{\color{black}
\subsection{Proofs of Collusion and Profit Trading Resistance}
We now show that Algorithm \ref{alg:np} can not only resist collusion attacks (by achieving group strategyproofness), but also eradicate the possibility of any profit trading (by achieving $N$-truthfulness). Parametric Dependency Graph (PDG) will be used to judge whether the strategyproof equilibrium can be group strategyproof or $N$-truthful.

@@

%Firstly our mechanism can achieve group strategyproof and $N$-truthful equilibrium.

@@

%For any discrete crowdsensing game with user utility equation $u_i = p_i - \kappa_in_i$, the incentive mechanism given above can achieve group strategyproof and $N$-truthful equilibrium.

@@

{\bf Budget utilization}. We first consider the budget utilization ratio of our mechanism with different sizes of users. Figure \ref{fig:rho_n} gives the results. The budget utilization ratio decreases as the size of users grows, since the maximum payment $P_m$ will decrease given more participating users ($N\cdot P_m$ is bounded by the budget $B$). In our mechanism, usually the budget utilization ratio is less than 16\%, which is budget-feasible. Repeating our mechanism may amplify the ratio. Since there are abundant budget, we can repeat the game many times.

@@

%This section will show our simulations that support the theoretic results we have obtained in the previous sections. Our crowdsensing incentive mechanism can achieve group strategyproof and $N$-truthful equilibrium simultaneously. 
